---
title: "FOR SOME REASON, THIS TOPS OUT AT 6 INTERACTIVE TABS RENDERING BACKWARDS"
output: flexdashboard::flex_dashboard
---
    
```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(flowmapblue)
library(htmltools)
library(knitr)

# rMarkdown parameters 
options(scipen = 999, digits = 3)

opts_chunk$set(
  cache = FALSE,
  warning = FALSE,
  echo = FALSE,
  message = FALSE,
  include = TRUE
)

# API Key 
source("../../API_KEYS/R/mapbox_key.R")

# Global Variables
clustered <- FALSE
floor <- 5

# Read Data
bilateral_international_migration <-
  read_csv("../clean/bilateral_international_migration.csv") %>%
  mutate(time = ymd_hms(time),
         time = as.integer(time) * 1000)

world_centroids <-
  read_csv("../clean/world_centroids.csv") %>% 
  select(id, lat, lon)

unique(bilateral_international_migration$category)

fn_map <- function(categories) {

  #categories <- "outward (minimisation:open)"
  
  df1 <- bilateral_international_migration %>%
    filter(category == categories) %>%
    filter(count > floor) %>%
    select(origin, dest, time, count)  
  
  flowmapblue(
    world_centroids,
    df1,
    mapbox_key,
    clustering = clustered,
    darkMode = TRUE,
    animation = FALSE
  )
}
```
    
Column {.tabset}
-------------------------------------

### outward (minimisation:open)

```{r}
#FOR SOME REASON, THIS TOPS OUT AT 6 INTERACTIVE TABS RENDERING BACKWARDS
fn_map("outward (minimisation:open)")
```   
 
### transit (minimisation:open)

```{r}
fn_map("transit (minimisation:open)")
```   

### return (minimisation:open)

```{r}
fn_map("return (minimisation:open)")
```   

### outward (minimisation:closed)

```{r}
fn_map("outward (minimisation:closed)")
```   

### transit (minimisation:closed)

```{r}
fn_map("transit (minimisation:closed)")
```   

### return (minimisation:closed)

```{r}
fn_map("return (minimisation:closed)")
```   

### outward (pseudo-Bayesian:closed)

```{r}
fn_map("outward (pseudo-Bayesian:closed)")
```   

### outward (minimisation:open)

```{r}
fn_map("transit (pseudo-Bayesian:closed)")
```   

### outward (minimisation:open)

```{r}
fn_map("return (pseudo-Bayesian:closed)")
```   

### source & instructions

This data is courtesy of: 

[Abel, G.J., Cohen, J.E. Bilateral international migration flow estimates for 200 countries. *Sci Data* 6, 82 (2019)](https://www.nature.com/articles/s41597-019-0089-3). [https://doi.org/10.1038/s41597-019-0089-3](https://doi.org/10.1038/s41597-019-0089-3) [data](https://figshare.com/collections/Bilateral_international_migration_flow_estimates_for_200_countries/4470464)

If you wish to look at one period at the time, shrink the width to include just one bar on the time line. Shrinking this to just within two bars will produce a smoother transition between the years.
